\documentclass[12pt]{book}

\usepackage[margin=0.8in]{geometry}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{float}
\usepackage{tgbonum}

\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{varwidth}



\pgfplotsset{width=10cm,compat=1.9}
\graphicspath{{./img}}

\usepgfplotslibrary{external}
\usetikzlibrary{calc}

\let\cleardoublepage=\clearpage

\newcommand\Chapter[2]{
  \chapter[#1: {\itshape#2}]{#1\\[2ex]\Large\itshape#2}
}

\newcommand{\changefont}{
    \fontsize{9}{11}\selectfont
}
\fancyhf{}

\fancyhead[L]{\changefont \slshape \leftmark\\}
\fancyhead[R]{\changefont \slshape \rightmark}
\fancyfoot[R]{\thepage}
\pagestyle{fancy}

\usepackage{lmodern}

\title{\textbf{My Preliminary Notes In Mathematics}}
\author{\textbf{By Erick Alejandro Carrillo López}}
\date{2024/05/30}

\begin{document}
\maketitle

\tableofcontents
\addcontentsline{toc}{chapter}{Contents}

\Chapter{Introduction}{The Purpuse of these Notes}
\include{chapters/introduction}

\Chapter{The Symbolism of Mathematics}{An Introduction to Algebra}
\include{chapters/symbolism}

\chapter{References}
\begin{itemize}
\item Murphy, P. A. (2021, february, 27). Who Says Nature is Mathematical? - cantor’s paradise. Cantor’s Paradise. https://www.cantorsparadise.com/who-says-nature-is-mathematical-1abdc1330224
\item ¿Qué es matemática? (2020, January 18) published by Matemáticas en Nuevo León.
\item Whitehead, A. N. (2022). An introduction to mathematics. Legare Street Press.
\item Courant, R., \& Robbins, H. (1979). What is mathematics?: An elementary approach to ideas and methods.
  Oxford University Press.
\item Baldor, A. (2017). Algebra (4nd ed.). Patria.xb
\item Guthrie, W. K. C. (1990). Los Filosofos Griegos: De Tales a Aristoteles. Fondo de Cultura Economica.
\end{itemize}


\end{document}



